---
title: "Welcome to the \"Data, Science, and Statistics\" blog"
author: "John D. Storey"
date: 2017-10-09
description: "Plans for my new blog." 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Yet another blog

Some of the most useful and inspiring research related ideas I've come across the last few years I found on blogs rather than in traditional publications. Blogs provide an opportunity to communicate ideas quickly, concisely, and with the flexibility and portability of a web site. I've benefitted tremendously from the time and effort that others have put into their blogs. I also find myself increasingly wanting to share ideas, tips, or examples that are best suited for a blog. So it's time for me to jump in and try to contribute to the blogosphere!

# Topics I plan to write about

Here are some topics I hope to cover:

- Data science as a field
- Key concepts in statistics
- Problems in genomics I'm excited about
- How I've taught two courses using R Markdown
- Techniques I use when analyzing data
- Data visualization approaches
- Tutorials on R packages I've developed
- Mixed martial arts analytics

I may also throw in a post occasionally that has nothing to do with data or science.

# How I created this blog

I used [blogdown](https://github.com/rstudio/blogdown), which utilizes [Hugo](https://gohugo.io) to create websites using [R Markdown](http://rmarkdown.rstudio.com). I'll therefore be able to include reproduicble R code and its output within my blog posts. For example...

```{r, results="hide"}
library("RXKCD")
getXKCD(552)
```